[dcpo_demsupport] Appendix

### 2020-07-15 paper/dcpo_demsupport_appendix.Rmd
add analysis of all 1000 draws (per https://github.com/fsolt/dcpo_dem_mood/issues/3#issuecomment-658743777); clean up

df_theta <- purrr::map(1:1000, function(x) {
  claassen_m5_theta$theta[x,,] %>% 
    as_tibble() %>% 
    rename_with(~ls_country, .cols = starts_with("V")) %>% 
    mutate(year = first_year + row_number() - 1) %>% 
    pivot_longer(cols = ls_country,
                 names_to = "country",
                 values_to = "theta") %>%
    arrange(country, year) %>% 
    left_join(df_controls, by = c("country" = "Country", "year" = "Year")) %>% 
    plm::pdata.frame(index = c("country", "year"))
})

>>>>

df_theta <- purrr::map(1:1000, function(x) {
  claassen_m5_theta$theta[1,,] %>% 
    as_tibble() %>% 
    rename_with(~ls_country, .cols = starts_with("V")) %>% 
    mutate(year = first_year + row_number() - 1) %>% 
    pivot_longer(cols = ls_country,
                 names_to = "country",
                 values_to = "theta") %>%
    arrange(country, year) %>% 
    left_join(df_controls, by = c("country" = "Country", "year" = "Year")) %>% 
    plm::pdata.frame(index = c("country", "year"))
})
